Verifying Demonstrations

### 2017-07-17 properties.tex
Adds some slides
Adds slides and notes for properties

\mode*
\section{Data authenticity and verification}

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous demonstrations.
  \item Alice must provide data which can be used for the desired verification 
    of the event.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the place the photo is portraying, however, this 
might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
This is discussed further in \cref{DataAuthenticity}.

@@

Now, consider the scenario of Alice taking a photo during the demonstration and 
posting it online.
What can we say about this photo?
First, we can say that it was created before we viewed it, so 
\cref{CreatedBeforeEnd} is fulfilled if we view it in relation to the event.
If it was submitted to a service that we trust, e.g.\ a blockchain, then we can 
also trust the time-stamp of the service for fulfilling 
\cref{CreatedBeforeEnd}.
Furthermore, we can also consider it spatially related to the physical location
(\cref{SpatiallyRelated}) if we can convince ourselves that the photo is 
depicting the physical location and not any kind of \enquote{reconstruction}, 
e.g.\ it is not computer generated or a photo of a similarly looking location.

\Cref{CreatedAfterStart} is more difficult to achieve.
In the above scenario, there is nothing that prevents Alice from submitting an 
older photo which is spatially related to the event --- i.e.\ to ensure 
\cref{CreatedAfterStart} we must ensure some sort of freshness.
% XXX Verify that this can be done using Fiat-Shamir heuristic
This can (probably) be solved using the Fiat--Shamir 
heuristic~\cite{FiatShamirHeuristic} (or something similar).
The main idea is that the operation binding the unpredictable value to the data 
must be difficult to redo later to change the value.

Instead of a photo, we will use \acp{LP}, more specifically, we will use 
\ac{PROPS}.
This will allow us to fulfil \cref{SpatiallyRelated}.
Since a location proof is a cryptographic value, it is easier to adapt it to 
fulfil \cref{CreatedAfterStart} too (compared to a photo).

@@

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
As was pointed out in the introduction, an online protest can be modelled as 
a petition, which in turn can use electronic voting protocols.
We are interested in translating these properties into a demonstration, i.e.\ 
a street-protest.

In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation (in either the protest 
or any counter-protest).
\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent any 
Sybil attack.

The three verifiability properties above are indeed desirable, e.g.\ then the 
\ac{UN} can verify protests happening in a country and the country cannot deny 
it, thus the \ac{UN} can apply pressure if needed.
However, these properties are difficult to accomplish with computer vision 
methods, especially if nobody that the \ac{UN} can trust has been on location 
to collect the image material for the analysis --- otherwise the authenticity 
can be questioned (as discussed in \cref{DataAuthenticity}).

We also need privacy in addition to the verification requirements.
In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the vote does not reveal any individual 
  vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
We can see that \cref{VotePrivacy,ReceiptFreeness} are desirable in Alice's 
situation: there should not be any proof which binds Alice to the participation 
of the demonstration (\cref{ReceiptFreeness}), because she does not want to 
explicitly reveal her opinions to the government (\cref{VotePrivacy}) due to 
the risk of reprimands.
\Cref{ReceiptFreeness} implies that even if Alice is arrested, the data should 
not provide any proof to the regime's agents that can reveal Alice's opinion.

>>>>

\mode*
\section{Authenticity, verification and privacy}

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous demonstrations.
  \item Alice must provide data which can be used for the desired verification 
    of the event.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the place the photo is portraying, however, this 
might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
This is discussed further in \cref{DataAuthenticity}.

@@

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedAfterStart}, after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the (hash of the) head of block chain.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{solution}

  \pause

  \begin{question}
    \begin{itemize}
      \item Is this hard?
      \item I think we can show that it is.
      \item What assumptions do we need for this?
    \end{itemize}
  \end{question}
\end{frame}

\begin{frame}<presentation>
  \begin{solution}[A\ref{CreatedBeforeEnd}, before end]
    \begin{itemize}
      \item Make the proof part of the block chain.
      \item The proof must've been created before it was included.
    \end{itemize}
  \end{solution}
\end{frame}

\begin{frame}<presentation>
  \begin{solution}[A\ref{SpatiallyRelated}, correct location]
    \begin{itemize}
      \item The proof includes \iac{LP}.
      \item The proof is \enquote{witnessed} (signed) by other participants.
      \item We have a coarse location, just within protest area.
    \end{itemize}
  \end{solution}

  \pause

  \begin{question}
    \begin{itemize}
      \item How can we do 1000s of \acp{LP} with 1000s of witnesses each?
    \end{itemize}
  \end{question}
\end{frame}

One primitive that provides the properties 
\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
consensus protocol.
\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
block chain in relation to the event.
For \cref{CreatedAfterStart} we must include an unpredictable value in the 
proof, e.g.\ the head of the block chain.

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.

@@

We have an adversarial setting between Alice the activist and Eve the evil 
regime: Alice wants to show large support against Eve, Eve wants to show little
support for Alice.
In this case we have two options:
either we trust Alice or Eve, or we must verify their claims.
We aim for verifiable claims.

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation.

If the proofs are included in a public block chain (as suggested in 
\cref{DataAuthenticity}), then an individual can check that their proof has 
been included in the chain.
Thus \cref{IndividualVerif} is fulfilled.

Anyone can count the proofs included in the block chain.
They can also verify the proofs and thus verify the result, which fulfils 
\cref{UniversalVerif}.

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.

\subsection{Privacy}
\label{Privacy}

We also need privacy in addition to the verification requirements.
In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the vote does not reveal any individual 
  vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\mode<presentation>{
\pause
\begin{remark}
  \begin{itemize}
    \item Coercion resistance is difficult to achieve for voting.
    \item It doesn't make much sense for protests.
    \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
      participate in.
  \end{itemize}
\end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
We can see that \cref{VotePrivacy,ReceiptFreeness} are desirable in Alice's 
situation: there should not be any proof which binds Alice to the participation 
of the demonstration (\cref{ReceiptFreeness}), because she does not want to 
explicitly reveal her opinions to the government (\cref{VotePrivacy}) due to 
the risk of reprimands.
\Cref{ReceiptFreeness} implies that even if Alice is arrested, the data should 
not provide any proof to the regime's agents that can reveal Alice's opinion.
